---
title: "Structural Equation Modelling of Political Trust and Ability"
author: "Max Savery"
date: "Academic year 2021-2022, 2nd semester\\`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output: bookdown::gitbook
geometry: margin=1in
bibliography: [sem.bib, packages.bib]
link-citations: yes
github-repo: saverymax/sem-political-trust
description: "Bookdown for structural equations project"
---
# Technical preface

This is the bookdown \citep{R-bookdown} report for the Structural Equations Modelling course. Bookdown was chosen 
as the medium for generating the report as part of my personal effort to support 
reproducible computational science. The lavaan package \citep{R-lavaan} was used for all structural equation models.

The bookdown report is hosted at <https://saverymax.github.io/sem-political-trust/>. The R/Rmd code for the report can be found here: <https://github.com/saverymax/sem-political-trust>. The plain R script to run 
all the code used in this report is available at <https://github.com/saverymax/sem-political-trust/blob/main/Max_Savery_SEM_project_code.R>

To locally render the book, install bookdown and run 
```
install.packages("bookdown")
bookdown::render_book('index.Rmd', 'bookdown::pdf_book')
```
That being said, given the time constraints of the semester and finishing my master's thesis, the bookdown report isn't perfect. But having a more-or-less well-documented and reproducible project
is better than not having one at all. I heavily relied on <https://github.com/rstudio/bookdown-demo> 
for setting it up.
```{r libs, include=FALSE}
library("dplyr")    
library("lavaan")    
library("corrplot")     
library("tidySEM")
library("kableExtra")
```
```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(.packages(), 'bookdown', 'knitr', 'rmarkdown'), 'packages.bib')
```
```{r env, include=FALSE}
#user_dir <- "d:/asus_documents/ku_leuven/courses/structural_equations/project/"
# Utils contains data processing function and defines dataset for global use.
#source(paste(user_dir, "sem_utils.R", sep=""), local = knitr::knit_global())
#source(paste(user_dir, "sem_functions.R", sep=""), local = knitr::knit_global())
source("sem_utils.R", local = knitr::knit_global())
source("sem_functions.R", local = knitr::knit_global())
```

