---
title: "Structural Equation Modelling of Political Trust and Ability"
author: "Max Savery"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output: bookdown::gitbook
geometry: margin=1in
bibliography: [sem.bib,packages.bib]
link-citations: yes
github-repo: saverymax/sem-political-trust
description: "Bookdown for structural equations project"
---
# Technical preface

This is the bookdown report for the Structural Equations Modelling course. Bookdown was chosen 
as the medium for generating the report as part of my personal effort to support 
reproducible computational science. 

The code for this report can be found at https://github.com/saverymax/sem-political-trust.
To render the book, run bookdown::render_book('index.Rmd', 'bookdown::pdf_book'). 
That being said, given the time constraints of the semester and finishing my master's thesis, the bookdown report isn't perfect.

It may also need to do setwd("d:/asus_documents/ku_leuven/courses/structural_equations/project/bookdown")

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

```{r libs, include=FALSE}
library("dplyr")      
library("lavaan")       
library("corrplot")     
library("tidySEM")
library("kableExtra")
```
```{r env, include=FALSE}
#user_dir <- "d:/asus_documents/ku_leuven/courses/structural_equations/project/"
# Utils contains data processing function and defines dataset for global use.
#source(paste(user_dir, "sem_utils.R", sep=""), local = knitr::knit_global())
source("sem_utils.R", local = knitr::knit_global())
#source(paste(user_dir, "sem_functions.R", sep=""), local = knitr::knit_global())
source("sem_functions.R", local = knitr::knit_global())
```

