# Mediation: political interest and ability
```{r load-4, include=FALSE}
df_subset <- data_processing(df)
```
Having developed a reliable measurement model for our constructs, we are now 
prepared to specify the structural part of our model.
Specifically, we consider a mediation model to explore the influence of political interest on political ability.
We include the indirect effect of political interest through government trust. We also consider the influence of 
trust in people on government trust.

what is the effect of political interest and trust in government 
on how people conceive of their ability to participate in politics?
Furthermore, is there a relationship between government trust and social trust?

The mediation model is written as 
\begin{verbatim}
    # Trust in government
    gov_trust =~ trstprl + trstprt + trstep + trstun
    # Trust in people
    people_trust =~ ppltrst + pplfair + pplhlp 
    # political ability
    political_able =~ psppipla + actrolga + psppsgva + cptppola
    # Add residual covariance
    actrolga ~~ cptppola
    trstep ~~ trstun
    # Add residual covariance
    trstep ~~ trstun
    trstprl ~~ trstep
    # Direct effect
    political_able ~ c1*polintr
    # Mediator
    # Path A
    gov_trust ~ a1*people_trust + a2*polintr
    # Path B
    political_able ~ b1*gov_trust
    # Indirect effect
    ab_trust := a1*b1
    ab_interest := a2*b1
    # Total effect
    total_interest := c1 + ab_interest
    total_trust := c1 + ab_trust
\end{verbatim}

```{r mediation, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
library("lavaan")
fit_med <- fit_mediation_model(df_subset)
caption <- "3-factor medidation model, considering structural relationship 
    between trust in people and trust in government"
label <- "three-fact-mediation"
print_fit(fit_med, caption, label)
```
Table \ref{tab:three-fact-mediation} shows the estimates for the mediation model.
We can see that the term \verb+ab\_interest := a2*b1+ is significant. Therefore, government trust
mediates between political interest and one's described ability to participate in 
the political system. Additionally, the total effect, \verb+total_interest+,  is significant, 
The model can be visualized below.
```{r graph-mediation, results='asis', echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Mediation model graph structure"}
graph_mediation(fit_med)
```


