# Modelling trust in government
```{r load-2, include=FALSE}
df_subset <- data_processing(df)
```

Here we investigate a CFA model for the latent factor representing trust in government, 
in order to determine the measurement component our our SEM model. We start with CFA 
for only the exogenous variables describing trust in government, because if 
we are not able to model these with a latent factor, the research question underlying this 
report will be a moot point.

We first fit a 1-factor CFA model with variables 
\begin{verbatim}
gov_trust =~ trstprl + trstprt + trstplt  + trstep + trstun
\end{verbatim}

Table \ref{tab:one-fact-trust} shows the standardized solution for the 1-factor model.
Note that this report will only present standardized solutions, for ease of interpretation of the
factor loadings, particularly the fact that the squared loadings are equal to the proportion of 
variance the latent factor explains in the indicator; however, standardized solutions are not always helpful
if it is necessary to understand linear relationships in terms of their original scale. 
Nonetheless, it can be seen that the standardized loadings are all greater than $0.6$. In fact, all loadings for trust in government institutions are quite high, with only trust in the U.N. somewhat lower at $0.66$. Furthermore, all loadings are positive,
indicating that as the score of the latent construct increases, so too do the 
exogenous variables.

```{r trust, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
library("lavaan")
fit_trust <- fit_trust_model(df_subset)
caption <- "1-factor CFA for trust in government"
label <- "one-fact-trust"
print_fit(fit_trust, caption, label)
caption <- "Modification indices for 1-factor model. Top 10 are shown."
label <- "one-fact-mi"
print_mi(fit_trust, caption, label)
```
We then examine the modification indices in Table \ref{tab:one-fact-mi}. Given the
high values for correlations involving the trstplt variable, we remove this variable, and add the residual covariance 
\verb+trstep ~~ trstun+. We refit this modified model, for which the standardized solution
is shown in Table \ref{tab:one-fact-trust-adj}. Table \ref{tab:one-fact-compare} 
compares the two models. It can be seen that the modified model
does in fact fit better, across all fit measures. At the onset of this work, 
it was not clear if the indicators for government trust could be represented 
with a latent factor. These results indicate that representing trust in government with a measurement model 
is indeed possible and produces reasonable factor scores for each indicator on the latent variable. Additionally, 
we can see that the model allowing for the covariances appears to be well-fitting, 
considering the $\chi^2$, CFI, TFI, and RMSEA measures.
```{r trust_adj, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
fit_trust_adj <- fit_trust_model_adj(df_subset)
caption <- paste("1-factor CFA for trust in government, allowing for residual covariances")
label <- paste("one-fact-trust-adj")
print_fit(fit_trust_adj, caption, label)
compare_one_factor(fit_trust, fit_trust_adj)
```
