# Introduction
```{r load-1, include=FALSE}
#data_file <- "ESS1-9e01_1/ESS1-9e01_1_all_dates.csv"
#user_dir <- "d:/asus_documents/ku_leuven/courses/structural_equations/project/"
#df <- read.csv(paste(user_dir, data_file, sep=""))
#df <- readr::read_csv(data_file)
df_subset <- data_processing(df)
```
This report focuses on the relationship between individual trust in government,
trust in others, and perceived ability to participate in the political system of one's country. We use 
the European Social Survey (ESS) data in this work, with only responses from round 9 \citep{ESS-2018}.
We split the variables into three categories, which will become our latent 
variables: Extent of trust in government or institutions, social trust (or general trust in people), and the extent to which people perceive it possible to participate in their country's political system. In a mediation analysis described later, we will also consider the effect of political interest
on poltical ability. The variables used in the analysis are shown in Table \ref{tab:var_desc}, with descriptions taken from the ESS documentation \citep{ESS-2021}.

\begin{table}[H]
    \centering
    \begin{tabular}{ll}
    \toprule
    Variable & Description \\
    \midrule
     Trust in people & \\
     PPLTRST & Most people can be trusted or you can't be too careful \\
     PPLFAIR & Most people try to take advantage of you, or try to be fair \\
     PPLHLP & Most of the time people helpful or mostly looking out for themselves \\
     \hline
     Poltical Ability &\\
     PSPPSGVA & Political system allows people to have a say in what government does \\
     ACTROLGA & Able to take active role in political group \\
     PSPPIPLA & Political system allows people to have influence on politics \\
     CPTPPOLA & Confident in own ability to participate in politics \\
     POLINTR & How interested in politics \\
     \hline
     Poltical Trust &\\
     TRSTPRL & Trust in country's parliament \\
     TRSTPLT & Trust in politicians \\
     TRSTPRT & Trust in political parties \\
     TRSTEP & Trust in the European Parliament \\
     TRSTUN & Trust in the United Nations \\
     \hline 
     \bottomrule
    \end{tabular}
    \caption{Selected variables from ESS and propsed latent constructs}
    \label{tab:var_desc}
\end{table}

Before we can begin with CFA and SEM, We first discuss the correlation present in the data. From the correlation plot \citep{R-corrplot} in Figure \ref{fig:exploratory}, it can be seen that there are high levels of correlation between the 
variables related to trust in government. This will likely affect our model specification later on,
when using the modification indices to choose which indicators to remove and which residual covariances to add. Interestingly, political interest (polintr) is highly negatively correlated with one's reported ability to actively participate in politics (actrolga) and one's confidence to do so (cptppola). This insight
will be important when we formulate the mediation model.
```{r exploratory, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Correlation between variables related to government trust, social trust, and poltical ability.", fig.align='center'}
exploratory_plots(df_subset)
```
