# Mediation: Trust in government
```{r load-4, include=FALSE}
df_subset <- data_processing(df)
```
Having developed a reliable measurement model for our constructs, we are now 
prepared to specify the structural part of our model.
Specifically, we consider a mediation model to explore the influence of political interest on political ability. We include the indirect effect of political interest through government trust. We also consider the influence of social trust on government trust. \citet{Zmerili-2008} find that there is a strong relationship
between these two trust-related factors, potentially in contrast to previous work at the individual level. They state, "The figures suggest that generalized social trust, political confidence, and satisfaction with democracy are indeed tied together in a tight three-cornered syndrome" (p. 719). While not considering satisfaction with democracy here, we are interested on the relationship between trust and political activity and participation. We mediate social trust through government trust because, as described in \citet{Kim-2014}, there is a positive relationship between trust in people and institutions. However, trust in individuals does not necessarily transfer directly to being more likely to 
engage in political activities. Therefore, mediation is suitable to model this relationship. 

The mediation model is written as 
\begin{verbatim}
    # Trust in government
    gov_trust =~ trstprl + trstprt + trstep + trstun
    # Trust in people
    people_trust =~ ppltrst + pplfair + pplhlp 
    # political ability
    political_able =~ psppipla + actrolga + psppsgva + cptppola
    # Add residual covariance
    actrolga ~~ cptppola
    trstep ~~ trstun
    # Direct effect
    political_able ~ c1*polintr + c2*people_trust
    # Mediator
    # Path A
    gov_trust ~ a1*people_trust + a2*polintr
    # Path B
    political_able ~ b1*gov_trust
    # Indirect effect
    ab_trust := a1*b1
    ab_interest := a2*b1
    # Total effect
    total_interest := c1 + ab_interest
    total_trust := c2 + ab_trust
\end{verbatim}
The model can be visualized in Figure \ref{fig:graph-mediation}.

```{r mediation, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
library("lavaan")
fit_med <- fit_mediation_model(df_subset)
caption <- "3-factor medidation model, considering structural relationship 
    between trust in people and trust in government"
label <- "three-fact-mediation"
print_fit(fit_med, caption, label)
print_med_fit_measures(fit_med)
```
Table \ref{tab:med-fit} shows the fit measures for the mediation model, which we find
to be adequate. Table \ref{tab:three-fact-mediation} shows the parameter estimates.
We can see that the indirect effect \verb+ab_interest+ is significant. Therefore, government trust
mediates between political interest and one's described ability to participate in 
the political system. However, the direct path from political interest to 
perceived political ability is also significant, meaning that political interest 
interacts with perceived political ability through both of these 
pathways. The coefficient for political interest between
government trust and political ability was negative in both cases, indicating that 
as political interest increases, trust in government and political ability decreases.
Furthermore, the total effect for political interest on political ability was negative
and significant. The reason for these negative relationships isn't necessarily clear, though it was also observed in the correlation plot in Figure \ref{fig:exploratory}. 

While it may be the case that individuals who are more politically interested may be more likely to participate in
politics, this doesn't necessarily mean they will trust the political system or the government
institutions more. In fact, higher political interest could indicate more awareness of
political issues and thus more skepticism of the political system or processes, depending on the country.
Given the negative correlation between political interest and both latent factors (government trust and poltical ability), the relationship merits more investigation.

The indirect effect of social trust, \verb+ab_trust+, is also significant. 
This indicates that government trust mediates this effect. Additionally, the direct effect
of social trust on political ability is insignificant. In this case, social trust only
affects political ability through government trust. This is somewhat reasonable: 
While people who are more trusting in general may be more likely to trust institutions,
there may not be any relationship between the tendency to trust people and the tendency to 
believe in the effectiveness of actions taken through the political system. However, people who
trust institutions could be much more likely to believe that they can effect 
change through these institutions. Of course, this will be highly dependent on the country 
and political system of interest.

```{r graph-mediation, results='asis', echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Mediation model graph structure", fig.align='center'}
graph_mediation(fit_med)
```
