# Political ability and trust
```{r load-3, include=FALSE}
df_subset <- data_processing(df)
```
We next specify the measurement model for perceived political ability, social trust, 
and government trust. We consider political ability, trust in others, and trust
in government to be the three factors in our CFA model. The fit of the model is shown in Table \ref{tab:three-fact-poli}.
It can be seen that all indicators have relatively high loadings on their respective latent factors, 
the lowest of which being actrolga with a loading of 0.5226, thereby indicating that the latent factors
of this measurement model are adequately accounting for the correlation in the data.
\begin{verbatim}
    # Trust in government
    gov_trust =~ trstprl + trstprt + trstplt  + trstep + trstun
    # Trust in people
    people_trust =~ ppltrst + pplfair + pplhlp 
    # Political ability
    political_able =~ psppipla + actrolga + psppsgva + cptppola
\end{verbatim}
```{r political, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
library("lavaan")
library("dplyr")
fit_politics <- fit_politics_model(df_subset)
caption <- "3-factor model for trust in government, trust in people, and political ability"
label <- "three-fact-poli"
print_fit(fit_politics, caption, label)
```
Considering that perhaps trust (government and social) could be represented
by a single factor, we compare the 3-factor model to a collapsed
2-factor model. The fit of the 2-factor model is shown in Table \ref{tab:two-fact-poli}.
Right away, it appears that the 2-factor model is not correctly handling the correlation 
in the data, because the loadings for the indicators relating to social trust have 
relatively low loadings on the trust construct. 
\begin{verbatim}
    # Trust 
    trust =~ trstprl + trstprt + trstplt + trstep + trstun + ppltrst + pplfair + pplhlp 
    # Political ability
    political_able =~ psppipla + actrolga + psppsgva + cptppola
\end{verbatim}

As these are nested models \citep{Brown-2006}\footnote{\citet{Brown-2006} states that while these can be considered nested models, there is some disagreement about the extent to which models with different numbers of latent factors are indeed nested.}, we can test the difference between them with a $\chi^2$ difference test, shown in Table \ref{tab:collapse-compare}. The models are significantly different, indicating that the 3-factor model significantly improves the fit.
```{r political-collapse, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
fit_coll <- fit_politics_collapsed(df_subset)
caption <- "Collapsed model, where trust becomes 1 factor"
label <- "two-fact-poli"
print_fit(fit_coll, caption, label)
```
```{r poli-compare, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
compare_poli(fit_politics, fit_coll)
caption <- "Modification indices for i model. Top 10 are shown."
label <- "three-fact-mi"
print_mi(fit_politics, caption, label)
```
We then compare the fit measures between the two models, shown in Table \ref{tab:three-fact-compare}.
It can be seen that the 3-factor model has a better goodness-of-fit. However,
the fit is not completely satisfactory, as the TFI and CLI are low while the RMSEA is somewhat
high. Therefore, we proceed to improve the 3-factor model. The modification 
indices for this model are shown in Table \ref{tab:three-fact-mi}. 
Following the bread crumbs left by the perturbations with the highest modification indices, 
we attempt to improve the fit by removing the variable trstplt. This was already done
once, when fitting the one-factor model, with good results. We also 
add the residual covariances 
\begin{itemize}
    \item \verb+actrolga ~~ cptppola+
    \item \verb+trstep ~~ trstun+
\end{itemize}
so that the model becomes
\begin{verbatim}
    # Trust in government
    gov_trust =~ trstprl + trstprt + trstep + trstun
    # Trust in people
    people_trust =~ ppltrst + pplfair + pplhlp 
    # Political ability
    political_able =~ psppipla + actrolga + psppsgva + cptppola
    # Add residual covariance
    actrolga ~~ cptppola
    trstep ~~ trstun
\end{verbatim}

The estimates for this model can be seen in Table \ref{tab:three-fact-mod-1}.

```{r improved-political, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
fit_adj_1 <- fit_improved_politics_model(df_subset)
caption <- paste("Modified 3-factor model for trust in government, trust in people, and political ability. Residual covariances are added and trstplt is removed.")
label <- paste("three-fact-mod-1")
print_fit(fit_adj_1, caption, label)
caption <- paste("After the first set of model changes, we consider again the modification 
                     indices for the 3-factor model. Top 10 are shown.")
label <- paste("three-fact-mi-2")
print_mi(fit_adj_1, caption, label)
```
We then reconsider the modification indices, in Table \ref{tab:three-fact-mi-2}.
From this, we add the indicator trstep into the regression relationship with social trust
and add the residual covariance \verb+trstprt ~~ trstep+. 
The cross-loading of trstep onto social trust is interesting because there certainly 
could be a directional relationship between the extent to which people trust in institutions such 
as the European Union and the extent to which they trust in others.
We again refit the model, and show the estimates in Table \ref{tab:three-fact-mod-2}. 
It can be seen that the cross-loading for trstep on the social trust latent factor is small and negative.
We take this to mean that while there is an interesting relationship between trust in the
European parliament and social trust, it is not correctly represented in the specification
of the measurement model here, and potentially could be part of a structural relationship.

The fit measures of the original 3-factor model and the two modified models are shown in Table \ref{tab:mod-three-fact-compare}. 
While both modified models provide a much better fit than the original, 
the second set of modifications appears to make only a marginal difference.
Given the small negative loading of trstep on social trust, we proceed with the model 
with only the first set of modifications. This model will be used in our mediation analysis.
```{r improved-political-2, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
fit_adj_2 <- fit_improved_politics_model_2(df_subset)
caption <- paste("Modified 3-factor model for trust in government, trust in people, and political ability. 
                 cross-loading for trstep is added, as well as new residual covariance")
label <- paste("three-fact-mod-2")
print_fit(fit_adj_2, caption, label)
# Compare all 3 models
compare_poli_adj(fit_politics, fit_adj_1, fit_adj_2)
```
The model can be visualized below.
```{r graph-model, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
graph_model(fit_adj_1)
```
