# Poltical ability and trust

We next model the relationship between perceived political ability, personal trust
of people, and government trust. We consider political ability, trust in others, and trust
in government to be the three factors in our CFA model. The fit of the model is shown in Table \ref{tab:three-fact-poli}
\begin{verbatim}
    # Trust in government
    gov_trust =~ trstprl + trstprt + trstplt  + trstep + trstun
    # Trust in people
    people_trust =~ ppltrst + pplfair + pplhlp 
    # Poltical ability
    poltical_able =~ psppipla + actrolga + psppsgva + cptppola
\end{verbatim}
```{r political, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
library("lavaan")
library("dplyr")
fit_politics <- fit_politics_model(df_subset)
caption <- "Three-factor model for trust in government, trust in people, and political ability"
label <- "three-fact-poli"
print_fit(fit_politics, caption, label)
```
Considering that perhaps trust (government and social) could be represented
by a single factor, We compare the three-factor model to a collapsed
two-factor model. The fit of the two-factor model is shown in Table \ref{tab:two-fact-poli}.
\begin{verbatim}
    # Trust 
    gov_trust =~ trstprl + trstprt + trstplt + trstep + trstun + ppltrst + pplfair + pplhlp 
    # Poltical ability
    poltical_able =~ psppipla + actrolga + psppsgva + cptppola
\end{verbatim}

To test the difference between these models, we conduct a likelihood ratio test, shown in Table \ref{tab:collapse-compare}. The models are significantly different, 
indicating that the two-factor model is not sufficient to represent the latent structure.
```{r political-collapse, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
fit_coll <- fit_politics_collapsed(df_subset)
caption <- "Collapsed model, where trust becomes 1 factor"
label <- "two-fact-poli"
print_fit(fit_coll, caption, label)
```

We then compare the fit measures between the two models, shown in Table \ref{tab:three-fact-compare}
It can be seen that the three-factor model has a better goodness-of-fit.
```{r poli-compare, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
compare_poli(fit_politics, fit_coll)
caption <- "Modification indices for three-factor model. Top 10 are shown."
label <- "three-fact-mi"
print_mi(fit_politics, caption, label)
```
We next consider how we can improve the three-factor model. The modification 
indices for this model are shown in Table \ref{tab:three-fact-mi}. 
Following the perturbations with the highes modification indices, 
we attempt to improve the fit by removing the variable trstplt. We also 
add the residual covariances 
\begin{itemize}
    \item \verb+trstep ~~ trstun+
    \item \verb+trstprl ~~ trstep+
    \item \verb+actrolga ~~ cptppola+
\end{itemize}
so that the model becomes
\begin{verbatim}
    # Trust in government
    gov_trust =~ trstprl + trstprt + trstep + trstun
    # Trust in people
    people_trust =~ ppltrst + pplfair + pplhlp 
    # Poltical ability
    poltical_able =~ psppipla + actrolga + psppsgva + cptppola
    # Add residual covariance
    trstep ~~ trstun
    trstprl ~~ trstep
    actrolga ~~ cptppola
\end{verbatim}

The estimates for this model can be seen in Table \ref{tab:three-fact-mod-1}.

```{r improved-political, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
fit_adj_1 <- fit_improved_politics_model(df_subset)
caption <- paste("Modified three-factor model for trust in government, trust in people, and political ability. Residual covariances are added and trstplt is removed.")
label <- paste("three-fact-mod-1")
print_fit(fit_adj_1, caption, label)
caption <- paste("After the first set of model changes, we consider again the modification 
                     indices for the three-factor model. Top 10 are shown.")
label <- paste("three-fact-mi-2")
print_mi(fit_adj_1, caption, label)
```
We then reconsider the modification indices, in Table \ref{tab:three-fact-mi-2}.
From this, we remove the indicator \verb+actrolga+ and the associated residual
covariance \verb+actrolga ~~ cptppola+. We again refit the model, and show the estimates
in Table \ref{tab:three-fact-mod-2}. The fit measures of the two modified models are 
shown in Table \ref{tab:mod-three-fact-compare}. However, the second set of modifications
appears to make little difference.
```{r improved-political-2, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
fit_adj_2 <- fit_improved_politics_model_2(df_subset)
caption <- paste("Modified three-factor model for trust in government, trust in people, and political ability. Variable actrolga is removed, as well as its associated covariance.")
label <- paste("three-fact-mod-2")
print_fit(fit_adj_2, caption, label)
compare_poli_adj(fit_adj_1, fit_adj_2)
```
The model can be visualized below.
```{r graph-model, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
graph_model(fit_adj_2)
```
